---
title: "Paper plots"
output: html_notebook
---

## Import data and run iAFM for plotting
```{r}
#set wd
rm(list=ls())
setwd("/Users/paulo/GitRepos/learning_rate/")

#load packages
library(ggplot2)
library(lme4)
library(data.table)

#load functions
source(file="models_function.R")

#datasets
datasets = fread("datasets.csv")

#dataset
dataset = datasets$StudentStep[1]
kcm = datasets$KC[1]
response = "First Attempt"
opportunity = datasets$Opportunity[1]
individual = "Anon Student Id"

#model
m <- iAFM(dataset,kcm,response,opportunity,individual)
```

## Get tables with data and convert to correct scale
```{r}
ds_student <- m$stud.params
ds_kc <- m$kc.params
ds_overall <- m$overall.params

ds_student$Intercept <- as.numeric(as.character(ds_student$Intercept))
ds_student$Slope <- as.numeric(as.character(ds_student$Slope))

ds_kc$Intercept <- as.numeric(as.character(ds_kc$Intercept))
ds_kc$Slope <- as.numeric(as.character(ds_kc$Slope))

ds_overall$maineffect_intercept <- as.numeric(as.character(ds_overall$maineffect_intercept))
ds_overall$maineffect_slope <- as.numeric(as.character(ds_overall$maineffect_slope))

ds_student$Intercept_corre <- ds_student$Intercept + ds_overall$maineffect_intercept
ds_student$Slope_corre <- ds_student$Slope + ds_overall$maineffect_slope
ds_student$initial_performance <- 1/(1+exp(-ds_student$Intercept_corre))
ds_student$med_initial <- median(ds_student$initial_performance)
ds_student$x <- median(ds_student$initial_performance)

ds_kc$Intercept_corre <- ds_kc$Intercept + ds_overall$maineffect_intercept
ds_kc$Slope_corre <- ds_kc$Slope + ds_overall$maineffect_slope
ds_kc$initial_performance <- 1/(1+exp(-ds_kc$Intercept_corre))
ds_kc$med_initial <- median(ds_kc$initial_performance)

df <- as.data.table(m$df)
sumdf <- df[,.(success=mean(success)),by=.(opportunity)]
sumdf <- sumdf[-which(is.na(sumdf$opportunity)),]
sumdf$opportunity <- sumdf$opportunity+1
```


## Plot a line for each student fixing intercept at the median intercept
```{r}
d_1 <- do.call("rbind", replicate(length(unique(ds_student$Student)), sumdf, simplify = FALSE))
Student <- sort(rep(ds_student$Student,length(unique(sumdf$opportunity))))

d_2 <- cbind(d_1,Student)

db <- merge(ds_student,d_2)

ggplot(data=db,
   aes(opportunity,success))+
  theme_bw() +
  scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(1,max(db$opportunity)),breaks = unique(db$opportunity)) +
  geom_abline(data=db,aes(slope=Slope_corre,intercept=med_initial,color=factor(Student))) + theme(legend.position = "none")

ggplot(data=db,
   aes(opportunity,success))+
  theme_bw() +
  scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(1,max(db$opportunity)),breaks = unique(db$opportunity)) +
  geom_abline(data=db,aes(slope=Slope_corre,intercept=initial_performance,color=factor(Student))) + theme(legend.position = "none")
```

## Plot a line for each KC fixing intercept at the median intercept
```{r}
d_1 <- do.call("rbind", replicate(length(unique(ds_kc$KC)), sumdf, simplify = FALSE))
KC <- sort(rep(ds_kc$KC,length(unique(sumdf$opportunity))))

d_2 <- cbind(d_1,KC)

db_2 <- merge(ds_kc,d_2)

ggplot(data=db_2,
   aes(opportunity,success))+
  theme_bw() +
  scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(1,max(db$opportunity)),breaks = unique(db$opportunity)) +
  geom_abline(data=db_2,aes(slope=Slope_corre,intercept=med_initial,color=factor(KC))) + theme(legend.position = "none")

ggplot(data=db_2,
   aes(opportunity,success))+
  theme_bw() +
  scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(1,max(db$opportunity)),breaks = unique(db$opportunity)) +
  geom_abline(data=db_2,aes(slope=Slope_corre,intercept=initial_performance,color=factor(KC))) + theme(legend.position = "none")
```
## notes
## use the table of interecepts and slopes to calculate opportunities backwords to find how far behind students reached the min intercept success rate
## scale things such that 1 is the first opportunity of the worst student, add from there.

## Plot lines squashing
```{r}
df_sum_student <- df[,.(accuracy=mean(1-predicted_error_rate)),by=.(opportunity)]
df_sum_student <- df_sum_student[!is.na(df_sum_student$opportunity)]
df_sum_student$opportunity <- as.numeric(df_sum_student$opportunity)
df_sum_student <- df_sum_student[df_sum_student$opportunity<6,]

ggplot(data=df_sum_student,
   aes(opportunity,accuracy,colour=individual))+
  theme_bw() + geom_line() + theme(legend.position = "none")
```
```{r}
newData <- data.table("opportunity"=c(rep(0,length(unique(df$individual))),rep(1,length(unique(df$individual))),rep(2,length(unique(df$individual))),rep(3,length(unique(df$individual))),rep(4,length(unique(df$individual))),rep(5,length(unique(df$individual))),rep(6,length(unique(df$individual))),rep(7,length(unique(df$individual))),rep(8,length(unique(df$individual))),rep(9,length(unique(df$individual))),rep(10,length(unique(df$individual))),rep(11,length(unique(df$individual))),rep(12,length(unique(df$individual))),rep(13,length(unique(df$individual))),rep(14,length(unique(df$individual))),rep(15,length(unique(df$individual)))),"individual"=rep(unique(df$individual),16),"KC"=rep("new",length(unique(df$individual))*16))

newData$pred <-predict(m$model,newData,type="response",allow.new.levels=TRUE,)

ggplot(data=newData,
   aes(opportunity,pred,colour=individual))+
  theme_bw() + geom_line() + theme(legend.position = "none")

newData$pred_lodds <- log(newData$pred/(1-newData$pred))

ggplot(data=newData[newData$opportunity<11,],
   aes(opportunity,pred_lodds,colour=individual))+
  theme_bw() + geom_line() + theme(legend.position = "none") + scale_y_continuous(name = "Performance (Log Scale)", breaks = c(-3,-2,-1,0,1,2,3), labels = c(0.04,0.12,0.27,0.50,0.73,0.88,0.95)) + scale_x_continuous(name = "Opportunity", breaks = c(0,1,2,3,4,5,6,7,8,9,10), labels = c(0,1,2,3,4,5,6,7,8,9,10)) + ggtitle("(B) Student Learning Rate")


```



```{r}
newData_kc <- data.table("opportunity"=c(rep(0,length(unique(df$KC))),rep(1,length(unique(df$KC))),rep(2,length(unique(df$KC))),rep(3,length(unique(df$KC))),rep(4,length(unique(df$KC))),rep(5,length(unique(df$KC))),rep(6,length(unique(df$KC))),rep(7,length(unique(df$KC))),rep(8,length(unique(df$KC))),rep(9,length(unique(df$KC))),rep(10,length(unique(df$KC))),rep(11,length(unique(df$KC))),rep(12,length(unique(df$KC))),rep(13,length(unique(df$KC))),rep(14,length(unique(df$KC))),rep(15,length(unique(df$KC)))),"KC"=rep(unique(df$KC),16),"individual"=rep("new",length(unique(df$KC))*16))

newData_kc$pred <-predict(m$model,newData_kc,type="response",allow.new.levels=TRUE,)

newData_kc$pred_lodds <- log(newData_kc$pred/(1-newData_kc$pred))

ggplot(data=newData_kc[newData_kc$opportunity<11,],
   aes(opportunity,pred_lodds,colour=KC))+
  theme_bw() + geom_line() + theme(legend.position = "none") + scale_y_continuous(name = "Performance (Log Scale)", breaks = c(-3,-2,-1,0,1,2,3), labels = c(0.04,0.12,0.27,0.50,0.73,0.88,0.95),limits = c(-3,3)) + scale_x_continuous(name = "Opportunity", breaks = c(0,1,2,3,4,5,6,7,8,9,10), labels = c(0,1,2,3,4,5,6,7,8,9,10)) + ggtitle("(A) KC Learning Rate")

```

